A Detection of the Environmental Dependence of the Sizes and Stellar Haloes of Massive Central Galaxies

### 2017-11-16 draft/paper2_v6.tex
Minor changes

% Commenting:
\newcommand{\xxx}[1]{\textcolor{red}{\textbf{XXX}}}
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:~#1}}}
\newcommand{\plan}[1]{\textcolor{cyan}{#1}}
\newcommand{\addref}{{\textcolor{red}{REF}}}
\newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
\newcommand{\song}[1]{\textcolor{magenta}{\textbf{[Song: #1]}}}
\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
\newcommand{\jenny}[1]{\textcolor{Bittersweet}{\textbf{[Jenny: #1]}}}
\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
\newcommand{\update}[1]{\textcolor{PineGreen}{#1}}

@@

    We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
    (median 0.6\asec seeing) imaging data from the Hyper Suprime--Cam (HSC) survey 
    to investigate the halo mass dependence of the surface mass density profiles 
    and outer stellar envelopes of massive galaxies. 
    The $i$-band images from HSC survey reach ${\sim}4$ magnitudes deeper than SDSS 
    and enable us to directly trace stellar mass distributions to 100 kpc without 
    requiring stacking.  
    We conclusively show that at fixed stellar mass, the stellar profiles of massive 
    galaxies depend on the masses of their dark matter halos. 
    On average, massive central galaxies with \logmtot{}$>11.6$ in more massive halos 
    at $0.3 < z < 0.5$ have shallower inner stellar mass density profiles 
    (within ${\sim}10$-$20$ kpc) and more prominent outer envelopes. 
    These differences translate into a halo mass dependence of the 
    mass--size relation: central galaxies in halos with \logmh{}$>14.0$ are 
    $\sim 20$\% larger in $R_{\mathrm{50}}$ at fixed \mtot{}.  
    Such dependence is also reflected in the relationship between the stellar mass 
    within 10 and 100 kpc. 
    Comparing to the mass--size relation, the \mtot{}--\minn{} relation avoids the 
    ambiguity in the definition of size, and can be straightforwardly compared with 
    simulations. 
    Our results demonstrate that, with deep images from HSC, we can quantify the 
    connection between halo mass and the outer stellar halo, which may provide new 
    constraints on the formation and assembly of massive central galaxies.

@@

    There have been multiple observational attempts to test the two-phase 
    formation scenario using galaxies at low redshift, by investigating surface 
    brightness or mass density profiles (e.g. \citealt{Huang2013a, Huang2013b, 
    Oh2017}, optical color gradients (e.g. \citealt{LaBarbera2010, LaBarbera2012}), 
    and stellar population gradients \citep[e.g.,][]{Coccato2010, Coccato2011, 
    Greene2015, Barbosa2016}. 
    Although these observations are generally consistent with the two-phase scenario, 
    this picture still faces a key puzzle: whether or not sizes and profiles of galaxies 
    depend on the mass of their host dark matter halos.

    According to the two-phase formation scenario, the late time growth of massive 
    ETGs is intrinsically tied to the growth of their host dark matter haloes 
    (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
    Massive ETGs living at the centers of more massive haloes should be subject to 
    higher merger rates compared to ETGs with similar stellar mass but living in less 
    massive dark matter haloes. 
    A natural prediction of this picture is therefore that the structures of 
    massive ETGs should depend on their ``environment''\footnote{There are 
    multiple definitions of ``environment'' in the literature.  
    In this work, we use ``environment'' and halo mass interchangeably.}.
    Theoretical models based on the two-phase formation scenario predict an 
    environmental dependence of the stellar mass--effective radius relation for 
    ETGs (\mstar{}--$R_{\rm e}$; 
    e.g., \citealt{Shen2003, Guo2009}): the sizes of massive ETGs in more massive 
    haloes should be larger than those in less massive haloes at fixed \mstar{} 
    (e.g. \citealt{Shankar2013, Shankar2014}). 
    Yet, solid evidence of this effect at low redshift is still missing 
    (e.g. \citealt{Nair2010, HCompany13}; but also see \citealt{Yoon2017}).

    %However, while hints of an environmental dependence in the mass-size relation have 
    %been spotted at high-$z$ (e.g. \citealt{Papovich2012, Lani2013, Delaye2014}; but 
    %also see \citealt{Rettura2010}).

	% Song: Actually the Illustris paper suggests that, for massive galaxies, 
	%       even the inner region is dominated by accreted stars.

    Testing this prediction requires deep imaging of ETGs in order to probe the 
    accreted component (the stellar halo) which can extend to 100 kpc and 
    beyond \citep[eg.,][]{hscMassiveI}. 
    This is observationally challenging as the surface brightness profiles of massive 
    ETGs decline rapidly with typical values of $\mu > 26.0$ \sb{} in $i$-band at 100 
    kpc and at $z\sim0.3$. 
    In \citet[][Paper I hereafter]{hscMassiveI}, we showed that deep, 
    multi-band imaging from the Subaru Strategic Program (SSP; \citealt{HSC-SSP,
    HSC-DR1}) using Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}, 
    Miyazaki in~prep.) allows us to extract robust surface stellar
    mass density (\mden{}) profiles for {\it individual} galaxies with 
    \logms{}$>11.4$ at $0.3 < z < 0.5$ and out to 100 kpc. 
    In Paper I, we characterized the stellar mass profiles of massive ETGs, and 
    showed that there is a large intrinsic scatter in the \mden{} stellar halos of
    massive galaxies on 100 kpc scales. 
    In this paper, we now investigate whether or not the large scatter in the outer 
    profiles of massive galaxies correlate with halo mass. 
    We conclusively show that the sizes and stellar halos of massive central galaxies 
    depend on dark matter halo mass. 
    In other terms, we reveal the halo mass dependence of the mass-size relation 
    for massive ETGs.

%    with the help of HSC images of a large sample 
%    of massive ETGs and the \redm{} cluster catalog (e.g.\ \citealt{Rykoff2014}; 
%    \citealt{Rozo2015b}; please see \S \ref{sec:data} for details)

@@

    In Paper~I, we select a sample of 25286 bright galaxies with spectroscopic 
    redshifts or reliable ``red-sequence'' photometric redshifts (\citealt{Rykoff2014}) 
    at $0.3<z<0.5$. 
    Within this redshift range, we have a large enough volume 
    ($\sim5\times 10^6$ Mpc$^3$) to sample the galaxy stellar mass function above 
    \logms$>11.6$, we can spatially resolve galaxies profiles to $\sim 5$ kpc 
    ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at $z=0.3$ and 0.5), and we can 
    safely ignore structural evolution over our redshift range ($\sim$1.5 Gyr of 
    time span).

@@

    In this work, we focus on massive galaxies with \mtot{} $>10^{11.6}$~\msun{}. 
    In Paper~I, we demonstrate that this sample is almost mass complete over our full 
    redshift range. 
    In addition to the mass cut above, we also limit our sample to galaxies that live 
    at the centers of their own dark matter haloes-- so-called ``central'' galaxies. 
    We use the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalog 
    to help us construct a central galaxy sample.

@@

    Firstly, we select 68 massive central galaxies from \redm{} clusters 
    with richness ($\lambda$) $\geq 30$, and the probability of true central galaxy 
    ($P_{\mathrm{Cen}}$) $\geq 0.7$, and \logmtot{}$>11.5$ 
    at $0.3 < z < 0.5$ (63/68 have \logmtot{}$>11.6$). 
    This $\lambda$ limit is chosen to mitigate incompleteness in the cluster catalog
    at the high end of our redshift window. 
    The $P_{\mathrm{Cen}}$ limit is selected to exclude low probability candidate of 
    central galaxy. 
    Based on the \mhalo{}-$\lambda$ relation calibrated by \citet{Simet2016}, these 
    correspond to central galaxies living in halos with \mhalo{}$>10^{14.2}$~\msun{}. 
    This calibration is consistent with other works (e.g. \citealt{Saro2015, Farahi2016, 
    Melchior2016, Murata2017}). 
    The median richness of the sample is $\lambda \approx 41$ 
    (\mhalo{}$\approx 2.2 \times 10^{14}$~\msun{}), and there are 
    only 44 central galaxies in clusters with $\lambda>50$ 
    (\mhalo{}$\approx 3.0 \times 10^{14}$~\msun{}).
    We will refer to this sample of \textbf{central galaxies in massive haloes} as 
    the \rbcg{} sample.

    Secondly, we build a complementary sample of central galaxies in lower-mass haloes
    by excluding all galaxies that are in any \redm{} cluster with $\lambda > 20$.
    We convert their $\lambda$ into $M_{\mathrm{200b}}$ using calibration by 
    \citet{Simet2016}. 
    Then we estimate the $R_{\mathrm{200b}}$ of each cluster using the method in 
    \citet{Diemer2015}. 
    We further exclude all galaxies within a cylinder around each cluster, with a radius
    equal to $R_{\mathrm{200b}}$ and a length equal to twice the value of the 
    photometric redshift uncertainty of the cluster (typically around 0.015 to 0.025).
    This second sample will be dominated by central galaxies living in haloes with
    $M_{\mathrm{200b}} < 10^{14}$~\msun{}, and will refer to this sample as \nbcg{}. \
    There are 833 galaxies with \logmtot{}$> 11.6$ in this sample.

%    Initially, we select 3453 galaxies this way with \logmtot{}$> 11.2$ at 
%    $0.3 < z < 0.5$ \alexie{Why do we care about this?}. 
%    Among them, 1564 (833) have \logmtot{}$> 11.5$ (11.6).

@@

    As shown in Figure~\ref{fig:m100_m10_color}, massive central galaxies at fixed  
    \minn{} display a large diversity in their stellar haloes. 
    In Paper~I, we explored the \mstar{}-dependence of the stellar haloes in massive 
    galaxies, and concluded that the general trends are consistent with the predictions 
    of the two-phase formation scenario. 
    In this work, we now investigate the relation between the \mden{} profiles of 
    massive galaxies, their stellar halos, and dark matter halo mass. 
    Here we use \mtot{} as proxy for the ``total'' \mstar{} of massive galaxies and 
    we use \minn{} as a rough proxy for the stellar mass of the \textit{in situ} 
    component.  
    We remind the reader that although a circular aperture is shown on 
    Fig~\ref{fig:m100_m10_color}, in practice we extract 1-D \mden{} profiles and 
    estimate \mtot{} and \minn{} using elliptical apertures following the average 
    fluxed-weighted isophotal shape.

@@

    The previous section clearly showed that the \mden{} profiles of massive central 
    galaxies depend on the masses of their host dark matter halos. 
    We now ask whether or not this dependence is also manifest when considered in 
    terms of the more traditionally studied \mstar{}--$R_{\mathrm{e}}$ relation. 
    However, when considering the mass-size relation, there is ambiguity and there are
    multiple approaches to define ``sizes''. 
    This is especially relevant in the context of massive galaxies with extended 
    stellar haloes (a reason why we prefer to show \mden{} profiles directly as in 
    the previous section). 
    In this section, we still use \mtot{} as proxy of ``total'' \mstar{} and we adopt 
    the radius enclosing 50\% of stellar mass within 100 kpc ($R_{\mathrm{50}}$; 
    derived from the $i$-band curve-of-growth) as the ``size''. 
    This definition of ``effective radius'' is more robust against structural details, 
    choice of model, and the background subtraction compared to the effective radius 
    estimated by simple 2-D modeling method (e.g. single-\ser{} model). 
    Massive galaxies from this sample are large enough that the impact of seeing is 
    not a concern.

    The left panel of Fig~\ref{fig:scaling_relation} shows the 
    \mtot{}--$R_{\mathrm{50}}$ relations for galaxies in more and less massive
    dark matter halos. 
    We fit the \logmtot{}-$\log (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
    $\log(M_{\star,100})>11.6$ using the \texttt{emcee} MCMC sampler 
    (\citealt{Emcee})\footnote{The initial guesses are based on maximum 
    likelihood estimates, and we assume flat priors for parameters.}.

@@

    We qualitatively compare our results with \citealt{HCompany13} (HC13; 
    green solid line) who studied $z\leq 0.09$ central ETGs in 
    $12.5 \le$ \logmh{} $< 15$ haloes. 
    HC13 use the group catalog by \citet{Yang2007} to estimate halo mass. 
    They obtain effective radii from single-\ser{} model fitting to SDSS 
    images and \mstar{} based on SED fitting using the BC03 (\citealt{BC03}) 
    synthetic population model. 
    We convert their \mstar{} estimates from a Kroupa IMF to a Chabrier 
    IMF by applying a constant -0.05 dex shift (see \citealt{Bernardi2016a}). 
    We further add $+0.1$dex to the HSC13 stellar masses to account for a systematic 
    offset between BC03 and our FSPS model (see Paper~1). 
    The distributions of galaxies on the 
    \mtot{}--$R_{\mathrm{50}}$ plane follow the HC13 relation reasonably well 
    (with slightly shallower slopes), even at \logmtot{}$< 11.6$ where our samples 
    start to become incomplete in stellar mass. 
    In contrast to the present study, HC13 finds no environment dependence in the 
    mass--size relation for central galaxies in the range $12.5\le$ \logmh{} $<15.0$.     
    Both the considerably shallower SDSS images and the single-\ser{} model could 
    contribute to this difference, since the most clear environmental differences 
    are found in the low surface brightness stellar halos that can not be 
    well-modeled with the inner portion of the \mden{} profile using single-\ser{}
    profiles.

@@

    These results are broadly consistent with the ``two-phase'' formation theory for 
    massive central galaxies.
    According to this scenario, intense dissipative processes at $z > 2$ are 
    responsible for the formation of \textit{in situ} stars in massive central 
    galaxies. 
    In the second phase, star-formation is quenched which limits in-situ star 
    formation and growth becomes dominated by non-dissipative mergers of satellite
    galaxies. 
    Dry minor mergers are efficient at depositing \textit{ex situ} stars in the 
    outskirts of massive galaxies (e.g. \citealt{Oogi2013, Bedorf2013}). 
    Because central galaxies in massive haloes should experience more mergers 
    compared to those in less massive halos, we expect the stellar mass profiles 
    (and sizes) of massive central galaxies to exhibit dependencies on host halo 
    mass.

    \citet{Shankar2014} studied the environment dependence of galaxy size using 
    a series of hierarchical semi-analytic models. 
    They predict that at fixed stellar mass, the median size of central galaxies 
    should increase strongly with halo mass. 
    The major-merger rate only increases slightly with halo mass (mass ratio $>1$:3; 
    e.g. \citealt{Hirschmann2013}). 
    The minor-merger rate, however, depends strongly on the dynamical friction time. 
    If the dynamical friction time is short (e.g. \citealt{Newman2012}), the
    massive central galaxies with $11.5 <$\logms{}$<12.0$ from more massive haloes 
    (\logmh{}$>14.0$) can have up to four times more minor mergers (1:100--1:3)
    compared to the ones in less massive halos at similar stellar mass. 
    This increase in the minor-merger rate as a function of halo mass leads to a 
    halo-mass dependence in the mass-size relation. 
    The predictions from \citet{Shankar2014} have been confirmed by \citet{Yoon2017} 
    using the semi-analytic model from \citet{Guo2011}.  
    Our results are broadly consistent with these predictions. 
    Indeed, we find that the outer profiles of massive galaxies ($r>50$ kpc) are the 
    regions that display the strongest variations as a function of halo mass.

@@

    Many previous works that focused on the mass-size relation found this relation 
    is independent of halo mass or environment at $z\sim 0.0$ 
    (e.g. \citealt{Nair2010, Maltby2010, Cappellari2013, HCompany13}). 
    As mentioned earlier, both the shallower imaging depth and the oversimple model 
    (e.g. single-\ser{} or de~Vaucouleurs model) used in the fitting can both 
    contribute to this difference.
    In Appendix~\ref{app:gama}, we use the \rbcg{} and \nbcg{} galaxies that overlap 
    with the GAMA survey to briefly demonstrate this point. 
    We show that, for galaxies with similar \mstar{} derived from single-\ser{} 
    models using shallower SDSS images (\citealt{Kelvin2012}), the ones in more 
    massive dark matter halos actually show more prominent outer stellar halos, 
    hence both of their stellar mass and effective radius are underestimated.  
    This shows again that the deeper HSC images has unique advantage in studying 
    the connection between the assembly of massive galaxies and their dark matter 
    haloes.

    At the same time, \citet{Cerbrian2014} find that ETGs with \logms{}$>11.5$ are 
    slightly larger in more massive haloes, and they also shows that this trend is 
    reversed at lower \mstar{}. 
    \citet{Yoon2017} present a careful study of a large sample of $z\sim0.1$ SDSS ETGs 
    using a non-parametric method and recover a clear environment dependence of 
    mass-size relation at \logms{}$>11.2$. 
    They conclude that, at the same \mstar{}, massive ETGs from dense environment 
    are 20--40\% larger compared to those in underdense environment.
    Recently, \citet{Charlton2017} uses single-\ser{} model for galaxies at 
    $0.2 < z < 0.8$ in the CFHTLenS (\citealt{Heymans2012}) and their galaxy--galaxy 
    lensing measurements to show that larger galaxies tend to live in more massive 
    dark matter haloes.
    These results are in broad agreement with those presented here.

>>>>

% Commenting:
\newcommand{\xxx}[1]{\textcolor{red}{\textbf{XXX}}}
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:~#1}}}
\newcommand{\plan}[1]{\textcolor{cyan}{#1}}
\newcommand{\addref}{{\textcolor{red}{REF}}}
\newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
\newcommand{\song}[1]{\textcolor{cyan}{#1}}
\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
\newcommand{\jenny}[1]{\textcolor{Bittersweet}{\textbf{[Jenny: #1]}}}
\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
\newcommand{\update}[1]{\textcolor{PineGreen}{#1}}

@@

    We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
    (median 0.6\asec seeing) imaging data from the Hyper Suprime--Cam (HSC) survey 
    to investigate the halo mass dependence of the surface mass density profiles 
    and outer stellar envelopes of massive galaxies. 
    The $i$-band images from HSC survey reach ${\sim}4$ magnitudes deeper than SDSS 
    and enable us to directly trace stellar mass distributions to 100 kpc without 
    requiring stacking.  
    We conclusively show that at fixed stellar mass, the stellar profiles of massive 
    galaxies depend on the masses of their dark matter haloes. 
    On average, massive central galaxies with \logmtot{}$>11.6$ in more massive haloes 
    at $0.3 < z < 0.5$ have shallower inner stellar mass density profiles 
    (within ${\sim}10$-$20$ kpc) and more prominent outer envelopes. 
    These differences translate into a halo mass dependence of the 
    mass--size relation: central galaxies in haloes with \logmh{}$>14.0$ are 
    $\sim 20$\% larger in $R_{\mathrm{50}}$ at fixed \mtot{}.  
    Such dependence is also reflected in the relationship between the stellar mass 
    within 10 and 100 kpc. 
    Comparing to the mass--size relation, the \mtot{}--\minn{} relation avoids the 
    ambiguity in the definition of size, and can be straightforwardly compared with 
    simulations. 
    Our results demonstrate that, with deep images from HSC, we can quantify the 
    connection between halo mass and the outer stellar halo, which may provide new 
    constraints on the formation and assembly of massive central galaxies.

@@

    There have been multiple observational attempts to test the two-phase 
    formation scenario using galaxies at low redshift, by investigating surface 
    brightness or mass density profiles (e.g. \citealt{Huang2013a, Huang2013b, 
    Oh2017}, optical color gradients (e.g. \citealt{LaBarbera2010, LaBarbera2012}), 
    and stellar population gradients \citep[e.g.,][]{Coccato2010, Coccato2011, 
    Greene2015, Barbosa2016}. 
    \song{
    These observations are generally consistent with the two-phase formation scenario. 
    However, it is still not clear whether this promising picture can correctly 
    predict the connection between the stellar mass distributions in massive galaxies 
    and their dark matter haloes.
    }

    \song{
    Under the $\Lambda$CDM cosmology, The assembly of massive ETGs is intrinsically 
    tied to the hierarchal growth of their host dark matter haloes 
    (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
    Hydrodynamic simulations suggest that the fraction of star accreted through 
    mergers (\textit{ex situ} component) in central galaxy increases with halo 
    mass (e.g. \citealt{Pillepich2017b}). 
    Although the major merger rate is not strong function of progenitor halo mass 
    (e.g. \citealt{Shankar2015}), minor mergers may still play a more important 
    role in the assembly of central galaxy of more massive dark matter halos 
    (e.g. \citealt{Guo2011, Yoon2017}). 
    As minor merger is more efficient at ``puffing up'' the outskirts of massive 
    galaxies (e.g. \citealt{Oogi2013, Bedorf2013}), this seems to suggest the 
    structures of massive ETGs and the well-known stellar mass--effective radius 
    relation (\mstar{}--$R_{\rm e}$; e.g., \citealt{Shen2003, Guo2009}) should depend 
    on their ``environment''\footnote{There are multiple definitions of 
    ``environment'' in the literature.  
    In this work, we use ``environment'' and halo mass interchangeably.}
    (e.g. \citealt{Shankar2013, Shankar2014}). 
    However, evidence for the environment--dependence of \mstar{}--$R_{\rm e}$
    at low redshift is still not very solid (\citealt{Nair2010, HCompany13}; 
    but also see \citealt{Yoon2017}), while the results at higher redshift are 
    even more confusing (e.g. \citealt{Papovich2012, Lani2013, Delaye2014}; but 
    also see \citealt{Rettura2010}).
    }

	\song{
    Therefore, we think it requires deeper images of these massive galaxies to 
    better probe their outer stellar mass distributions and test these 
    predictions. 
    Unfortunately, this is observationally challenging since the stellar haloes 
    of massive galaxies can extend to $>100$ kpc (e.g.\citealt{Tal2011, DSouza2014}),
    and their surface brightness profiles decline rapidly with typical values of 
    $\mu > 26.0$ \sb{} in $i$-band at 100 kpc and at $z\sim0.3$. 
    }
    In \citet[][Paper I hereafter]{hscMassiveI}, we showed that deep, 
    multi-band imaging from the Subaru Strategic Program (SSP; \citealt{HSC-SSP,
    HSC-DR1}) using Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}, 
    Miyazaki in~prep.) allows us to extract robust surface stellar
    mass density (\mden{}) profiles for {\it individual} galaxies with 
    \logms{}$>11.4$ at $0.3 < z < 0.5$ and out to 100 kpc. 
    In Paper I, we characterized the stellar mass profiles of massive ETGs, and 
    showed that there is a large intrinsic scatter in the \mden{} stellar haloes of
    massive galaxies on 100 kpc scales. 
    In this paper, we now investigate whether or not the large scatter in the outer 
    profiles of massive galaxies correlate with halo mass. 
    We conclusively show that the sizes and stellar haloes of massive central galaxies 
    depend on dark matter halo mass. 
    In other terms, we reveal the halo mass dependence of the mass-size relation 
    for massive ETGs.

@@

    In Paper~I, we select a sample of 25286 bright galaxies with spectroscopic 
    redshifts or reliable ``red-sequence'' photometric redshifts (\citealt{Rykoff2014}) 
    at $0.3<z<0.5$. 
    Within this redshift range, we have a large enough volume 
    ($\sim5\times 10^6$ Mpc$^3$) to sample the galaxy stellar mass function above 
    \logms$>11.6$, we can spatially resolve galaxies profiles to $\sim 5$ kpc 
    ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at $z=0.3$ and 0.5). 
    \song{
    And massive galaxies should experience little structural evolution and 
    size growth between $z=0.5$ and 0.3 ($\sim$1.5 Gyr of time span) 
    based on model prediction (e.g. \citealt{Shankar2015}).
    }

@@

    In this work, we focus on massive galaxies with \mtot{} $>10^{11.6}$~\msun{}. 
    In Paper~I, we demonstrate that this sample is almost mass complete over our full 
    redshift range. 
    In addition to the mass cut above, we also limit our sample to galaxies that live 
    at the centers of their own dark matter haloes-- so-called ``central'' galaxies. 
    We use the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalogue 
    to help us construct a central galaxy sample.

@@

    Firstly, we select 68 massive central galaxies from \redm{} clusters 
    with richness ($\lambda$) $\geq 30$, and the probability of true central galaxy 
    ($P_{\mathrm{Cen}}$) $\geq 0.7$, and \logmtot{}$>11.5$ 
    at $0.3 < z < 0.5$ (63/68 have \logmtot{}$>11.6$). 
    This $\lambda$ limit is chosen to mitigate incompleteness in the cluster catalogue
    at the high end of our redshift window. 
    The $P_{\mathrm{Cen}}$ limit is selected to exclude low probability candidate of 
    central galaxy. 
    \song{
    \citet{Simet2017} calibrates the \mhalo{}-$\lambda$ relation for the \redm{} 
    clusters using the SDSS weak lensing data after carefully addressing many 
    important systematic uncertainties.
    Based on this calibration, these correspond to central galaxies living in haloes 
    with \mhalo{}$>10^{14.2}$~\msun{}. 
    This calibration is consistent with several other independent calibrations 
    using different methods (e.g. \citealt{Saro2015, Farahi2016, 
    Melchior2016, Murata2017}). 
    }
    The median richness of the sample is $\lambda \approx 41$ 
    (\mhalo{}$\approx 2.2 \times 10^{14}$~\msun{}), and there are 
    only 44 central galaxies in clusters with $\lambda>50$ 
    (\mhalo{}$\approx 3.0 \times 10^{14}$~\msun{}).
    We will refer to this sample of \textbf{central galaxies in massive haloes} as 
    the \rbcg{} sample.

    Secondly, we build a complementary sample of central galaxies in lower-mass haloes
    by excluding all galaxies that are in any \redm{} cluster with $\lambda > 20$.
    \song{
    We convert their $\lambda$ into $M_{\mathrm{200b}}$ using calibration by 
    \citet{Simet2017}. 
    \citet{Diemer2015} systematically investigates the mass density profiles of 
    dark matter haloes under $\Lambda$CDM cosmology using a suite of dark matter--only
    simulations.  
    They provide empirical functions that describe the average density profiles 
    of dark matters with different halo mass and at different redshifts.  
    Using the \texttt{Colossus} Python package 
    (\citealt{Colossus})\footnote{\url{http://www.benediktdiemer.com/code/colossus/}}
    provided by these authors, we estimate the $R_{\mathrm{200b}}$ of each cluster 
    given its $M_{\mathrm{200b}}$ and redshift.
    } 
    We further exclude all galaxies within a cylinder around each cluster, with a radius
    equal to $R_{\mathrm{200b}}$ and a length equal to twice the value of the 
    photometric redshift uncertainty of the cluster (typically around 0.015 to 0.025).
    This second sample will be dominated by central galaxies living in haloes with
    $M_{\mathrm{200b}} < 10^{14}$~\msun{}, and will refer to this sample as \nbcg{}. \
    There are 833 galaxies with \logmtot{}$> 11.6$ in this sample.

@@

    As shown in Figure~\ref{fig:m100_m10_color}, massive central galaxies at fixed  
    \minn{} display a large diversity in their stellar haloes. 
    In Paper~I, we explored the \mstar{}-dependence of the stellar haloes in massive 
    galaxies, and concluded that the general trends are consistent with the predictions 
    of the two-phase formation scenario. 
    In this work, we now investigate the relation between the \mden{} profiles of 
    massive galaxies, their stellar haloes, and dark matter halo mass. 
    Here we use \mtot{} as proxy for the ``total'' \mstar{} of massive galaxies and 
    we use \minn{} as a rough proxy for the stellar mass of the \textit{in situ} 
    component.  
    We remind the reader that although a circular aperture is shown on 
    Fig~\ref{fig:m100_m10_color}, in practice we extract 1-D \mden{} profiles and 
    estimate \mtot{} and \minn{} using elliptical apertures following the average 
    fluxed-weighted isophotal shape.

@@

    The previous section clearly showed that the \mden{} profiles of massive central 
    galaxies depend on the masses of their host dark matter haloes. 
    We now ask whether or not this dependence is also manifest when considered in 
    terms of the more traditionally studied \mstar{}--$R_{\mathrm{e}}$ relation. 
    However, when considering the mass-size relation, there is ambiguity and there are
    multiple approaches to define ``sizes''. 
    This is especially relevant in the context of massive galaxies with extended 
    stellar haloes (a reason why we prefer to show \mden{} profiles directly as in 
    the previous section). 
    In this section, we still use \mtot{} as proxy of ``total'' \mstar{} and we adopt 
    the radius enclosing 50\% of stellar mass within 100 kpc ($R_{\mathrm{50}}$; 
    derived from the $i$-band curve-of-growth) as the ``size''. 
    This definition of ``effective radius'' is more robust against structural details, 
    choice of model, and the background subtraction compared to the effective radius 
    estimated by simple 2-D modeling method (e.g. single-\ser{} model). 
    Massive galaxies from this sample are large enough that the impact of seeing is 
    not a concern.

    The left panel of Fig~\ref{fig:scaling_relation} shows the 
    \mtot{}--$R_{\mathrm{50}}$ relations for galaxies in more and less massive
    dark matter haloes. 
    We fit the \logmtot{}-$\log (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
    $\log(M_{\star,100})>11.6$ using the \texttt{emcee} MCMC sampler 
    (\citealt{Emcee})\footnote{The initial guesses are based on maximum 
    likelihood estimates, and we assume flat priors for parameters.}.

@@

    We qualitatively compare our results with \citealt{HCompany13} (HC13; 
    green solid line) who studied $z\leq 0.09$ central ETGs in 
    $12.5 \le$ \logmh{} $< 15$ haloes. 
    HC13 use the group catalogue by \citet{Yang2007} to estimate halo mass. 
    They obtain effective radii from single-\ser{} model fitting to SDSS 
    images and \mstar{} based on SED fitting using the BC03 (\citealt{BC03}) 
    synthetic population model. 
    We convert their \mstar{} estimates from a Kroupa IMF to a Chabrier 
    IMF by applying a constant -0.05 dex shift (see \citealt{Bernardi2016a}). 
    We further add $+0.1$dex to the HSC13 stellar masses to account for a systematic 
    offset between BC03 and our FSPS model (see Paper~1). 
    The distributions of galaxies on the 
    \mtot{}--$R_{\mathrm{50}}$ plane follow the HC13 relation reasonably well 
    (with slightly shallower slopes), even at \logmtot{}$< 11.6$ where our samples 
    start to become incomplete in stellar mass. 
    In contrast to the present study, HC13 finds no environment dependence in the 
    mass--size relation for central galaxies in the range $12.5\le$ \logmh{} $<15.0$.     
    Both the considerably shallower SDSS images and the single-\ser{} model could 
    contribute to this difference, since the most clear environmental differences 
    are found in the low surface brightness stellar haloes that can not be 
    well-modeled with the inner portion of the \mden{} profile using single-\ser{}
    profiles.

@@

    \song{
    The two--phase formation scenario can qualitatively explain these results. 
    Under this picture, intense dissipative processes at $z > 2$ are 
    responsible for the formation of \textit{in situ} stars in massive central 
    galaxies. 
    After the star-formation was rapidly quenched by certain mechanism, the 
    assembly of massive galaxies in the second phase is dominated by accretion 
    of satellite galaxies through (mostly) non-dissipative mergers. 
    Dry minor mergers are efficient at depositing \textit{ex situ} stars in the 
    outskirts of massive galaxies (e.g. \citealt{Oogi2013, Bedorf2013}). 
    If minor mergers become more frequent in more massive dark matter halos, 
    they can result in slightly different stellar mass distributions and larger 
    effective radius for their massive central galaxies.
    }

    \citet{Shankar2014} studied the environment dependence of galaxy size using 
    a series of hierarchical semi-analytic models. 
    They predict that at fixed stellar mass, the median size of central galaxies 
    should increase strongly with halo mass. 
    \song{
    Although the major-merger rate does not strongly depend on halo mass 
    (mass ratio $>1$:3; e.g. \citealt{Hirschmann2013, Shankar2015}), minor 
    merger rate could still increase with halo mass if the dynamical friction time 
    is short (e.g. \citealt{Newman2012}). 
    Therefore, massive central galaxies with $11.5 <$\logms{}$<12.0$ from more massive 
    haloes (\logmh{}$>14.0$) can have up to four times more minor mergers (1:100--1:3)
    compared to the ones in less massive haloes at similar stellar mass. 
    Such increase in the minor-merger rate as a function of halo mass leads to a 
    halo-mass dependence in the mass-size relation. 
    }
    The predictions from \citet{Shankar2014} have been confirmed by \citet{Yoon2017} 
    using the semi-analytic model from \citet{Guo2011}.

    \song{
    Our results are broadly consistent with these predictions and also suggest that 
    the outer stellar haloes ($r>50$ kpc) of massive galaxies show the strongest 
    variations with halo mass. 
    At the same time, we should point out that comparison at low redshift alone 
    can not rule out some other scenarios.  
    For instance, \citet{Buchan2016} suggests that central galaxies in more massive 
    haloes could born with more extended structure. 
    More careful comparisons at higher redshift should help clarify these situations
    although recent observations of massive central galaxies of $z>2$ proto--clusters 
    seem to confirm their compact nature (e.g. \citealt{Kubo2017}).
    }

@@

    Many previous works that focused on the mass-size relation found this relation 
    is independent of halo mass or environment at $z\sim 0.0$ 
    (e.g. \citealt{Nair2010, Maltby2010, Cappellari2013, HCompany13}). 
    As mentioned earlier, both the shallower imaging depth and the oversimple model 
    (e.g. single-\ser{} or de~Vaucouleurs model) used in the fitting can both 
    contribute to this difference.
    In Appendix~\ref{app:gama}, we use the \rbcg{} and \nbcg{} galaxies that overlap 
    with the GAMA survey to briefly demonstrate this point. 
    We show that, for galaxies with similar \mstar{} derived from single-\ser{} 
    models using shallower SDSS images (\citealt{Kelvin2012}), the ones in more 
    massive dark matter haloes actually show more prominent outer stellar haloes, 
    hence both of their stellar mass and effective radius are underestimated.  
    This shows again that the deeper HSC images has unique advantage in studying 
    the connection between the assembly of massive galaxies and their dark matter 
    haloes.

    At the same time, \citet{Cerbrian2014} find that ETGs with \logms{}$>11.5$ are 
    slightly larger in more massive haloes, and they also show that this trend is 
    reversed at lower \mstar{}. 
    \citet{Yoon2017} present a careful study of a large sample of $z\sim0.1$ SDSS ETGs 
    using a non-parametric method and recover a clear environment dependence of 
    mass-size relation at \logms{}$>11.2$. 
    They conclude that, at the same \mstar{}, massive ETGs from dense environment 
    are 20--40\% larger compared to those in underdense environment.
    Recently, \citet{Charlton2017} uses single-\ser{} model for galaxies at 
    $0.2 < z < 0.8$ in the CFHTLenS (\citealt{Heymans2012}) and their galaxy--galaxy 
    lensing measurements to show that larger galaxies tend to live in more massive 
    dark matter haloes.
    These results are in broad agreement with those presented here.
